Manuscript Figures

### 2020-06-19 doc/MS_Figures_v2.rmd
new figure3, updated data files

# Fig 3

@@

Q1.SC.short.mouse_scatter_boxplot <- ggplot( Short.biv_mouse_table, aes(y = mean_SC, x = sex, color=strain)) + geom_jitter()+ geom_boxplot(alpha=.2) +scale_color_manual(values=colors_of_strains)+facet_wrap(~subsp, scales="free")+ylim(c(20,115) )+ggtitle("")+  
  theme(panel.grid.major = element_blank(), panel.grid.minor = element_blank(),
panel.background = element_blank(), axis.line = element_line(colour = "black"),  legend.position="none", axis.title.x = element_blank(), axis.text.x = element_text(size=7), axis.title.y = element_text(size = 10), axis.text.y = element_text(size=9) )+

  labs(y = "Short SC Length")

@@

Tot.SC_mouse.av_ALL <- ggplot(data= Q1.totSC.mouse.av.table, aes(y = mean.skel, x=sex, color=strain))+
  scale_color_manual(values=colors_of_strains)+
    facet_wrap(~subsp, scales="free", ncol = 3) +

  geom_jitter()+ geom_boxplot(alpha=.2)+ 
  #geom_hline(data =totSC.strain.av.table, aes(yintercept=mean.skel) )+

  theme(panel.grid.major = element_blank(), panel.grid.minor = element_blank(), panel.background = element_blank(), axis.line = element_line(colour = "black"),
    axis.title.x=element_blank(),
axis.text.x = element_text(size=7), 
legend.position="none",axis.text.y = element_text(size=9), # axis.text.y = element_blank()
axis.title.y = element_text(size = 10) ) +

  labs(y = "Total SC Length")+ylim(c(1000,5000 ))+ggtitle("")

ggsave("~/MLH1repo/doc/Figure3_Tot.SC_mouse.av_ALL.png")

#ggsave("~/MLH1repo/doc/Figure3_Q1.SC.short.mouse_scatter_boxplot.png")

>>>>

@@

Q1.SC.short.mouse_scatter_boxplot <- ggplot( Short.biv_mouse_table, aes(y = mean_SC, x = sex, color=strain)) +

     geom_boxplot(alpha=.5, outlier.shape = NA) +
  #Yeah, I can dodge the points!!
  geom_point(pch = 19, position = position_jitterdodge()) +

  scale_color_manual(values=colors_of_strains)+facet_wrap(~subsp, scales="free")+ylim(c(20,115) )+ggtitle("")+  
  theme(panel.grid.major = element_blank(), panel.grid.minor = element_blank(),
panel.background = element_blank(), axis.line = element_line(colour = "black"),  legend.position="none", axis.title.x = element_blank(), axis.text.x = element_text(size=7), axis.title.y = element_text(size = 10), axis.text.y = element_text(size=9) )+

  labs(y = "Short Bivalent Length")

@@

Tot.SC_mouse.av_ALL <- ggplot(data= Q1.totSC.mouse.av.table, aes(y = mean.skel, x=sex, color=strain))+
  scale_color_manual(values=colors_of_strains)+
    facet_wrap(~subsp, scales="free", ncol = 3) + 
    geom_boxplot(alpha=.5, outlier.shape = NA) +
  #Yeah, I can dodge the points!!
  geom_point(pch = 19, position = position_jitterdodge()) +

  #geom_hline(data =totSC.strain.av.table, aes(yintercept=mean.skel) )+

  theme(panel.grid.major = element_blank(), panel.grid.minor = element_blank(), panel.background = element_blank(), axis.line = element_line(colour = "black"),
    axis.title.x=element_blank(),
axis.text.x = element_text(size=7), 
legend.position="none",axis.text.y = element_text(size=9), # axis.text.y = element_blank()
axis.title.y = element_text(size = 10) ) + labs(y = "Total SC Length")+ylim(c(1000,2700 ))+ggtitle("")

#ggsave("~/MLH1repo/doc/Figure3_Tot.SC_mouse.av_ALL.png")
#ggsave("~/MLH1repo/doc/Figure3_Q1.SC.short.mouse_scatter_boxplot.png")
